Paper figures

### 2021-05-11 notebooks/paper_plots_1213_pcc_only.Rmd
more paper figures

```{r}
library(reticulate)
# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv("enm")
setwd("../")
source("src/R/plot_density_prs.R")
figure_path = 'reports/figures/0404_paperfigure_sensors/'
```

>>>>

```{r}
library(reticulate)
# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv("enm")
#setwd("../")
source("src/R/plot_density_prs.R")
figure_path = 'reports/figures/0404_paperfigure_sensors/'
```
